---
title: "COPD & Asthma 2020"
author: "Laura Dean & Dr. David Fong"
date: "25th March 2020"
output:
  html_document
bibliography: "My Library.bib"
always_allow_html: yes
link_citations: true
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## COPD & Asthma review benefits


## Extent of COPD & Asthma


## Current strategies to manage COPD & Asthma



# COPD & Asthma project

## Methods

* Identify COPD & Asthma

```{r message = FALSE, results = 'hide', warning = FALSE}
library(tidyverse)
library(lubridate)
library(xlsx)
library(openxlsx)
library(formattable)
library(kableExtra)
```

## Logframe



## Variables to measure

* **Age** in ten year age groups (age 50 to 89 years)
* **Sex**
* **Refugee or asylum seeker** Possible proxy for less English literacy skills, or different health literacy.
* **RespiratoryMedication** Listed as using respiratory medication
* **Smoking** Number of medications listed in record


## Potential outcome measures

* **Smoking**
* Number of discharge summaries (reflecting hospital admissions)
* Home Medication Reviews (HMR)
* Overall billing
* Overall billed visits
* Blood pressure - on target?

# Data and Code

## Read Data

```{r}
population <- as_tibble(read.xlsx2("../../PEN Clinical Audit/20200324_AsthmaCOPD patients.xlsx",
                                   startRow = 4, endRow = 353, sheetIndex = 1,
                                   colClasses = c(ID = 'numeric'),
                                   stringsAsFactors = FALSE))
names(population) <- gsub("\\.", "", names(population)) # remove periods '.'
population <- population %>%
  filter(!(Surname == "Test")) # get rid of the 'Test' patient!

refugeeorasylum <- as_tibble(read.csv("../../PEN Clinical Audit/20200206RefugeeAsylum.csv",
                                      stringsAsFactors = FALSE,
                                      colClasses = c(INTERNALID = 'numeric'))) %>%
  select(INTERNALID)

respiratory <- as_tibble(read.xlsx2("../../PEN Clinical Audit/202002MedicationRespiratory.xlsx",
                                    startRow = 4, sheetIndex = 1,
                                    colClasses = c(ID = 'numeric'),
                                    stringsAsFactors = FALSE))
names(respiratory) <- gsub("\\.", "", names(respiratory)) # remove periods '.'
respiratory <- respiratory[-nrow(respiratory),] %>%
  select(ID, Medications)

```

## Convert data

```{r}
# Calculate age
# 
# By default, calculates the typical "age in years", with a
# \code{floor} applied so that you are, e.g., 5 years old from
# 5th birthday through the day before your 6th birthday. Set
# \code{floor = FALSE} to return decimal ages, and change \code{units}
# for units other than years.
# @param dob date-of-birth, the day to start calculating age.
# @param age.day the date on which age is to be calculated.
# @param units unit to measure age in. Defaults to \code{"years"}. Passed to \link{\code{duration}}.
# @param floor boolean for whether or not to floor the result. Defaults to \code{TRUE}.
# @return Age in \code{units}. Will be an integer if \code{floor = TRUE}.
# @examples
# my.dob <- as.Date('1983-10-20')
# age(my.dob)
# age(my.dob, units = "minutes")
# age(my.dob, floor = FALSE)
# code by 'Gregor' 
# https://stackoverflow.com/questions/27096485/change-a-column-from-birth-date-to-age-in-r
# requires library 'lubridate'

age <- function(dob, age.day = today(), units = "years", floor = TRUE) {
  calc.age = interval(dob, age.day) / duration(num = 1, units = units)
  if (floor) return(as.integer(floor(calc.age)))
  return(calc.age)
}

population <- population %>%
  # add columns for whether they have seen the doctor who is making the telephone calls
  # or are of known refugee or asylum seeker background
  # (?proxy for low English language literacy)
  mutate(RefugeeOrAsylum = ID %in% refugeeorasylum$INTERNALID,
         respiratory = ID %in% respiratory$ID,
         DOB = as.Date(substr(DOBAge, 1, 10), format = "%d/%m/%Y")) %>% 
  mutate(Age = age(DOB, age.day = as.Date("2020/02/01"))) %>%
  # note that age is on 1st Feb 2020
  mutate(AgeGroup10 = ((Age %/% 10)*10),
         AgeGroup5 = ((Age %/% 5)* 5)) # 5 and 10-year age groups, labelled with minimum age

population %>%
  select(c(DOB, Age, Sex, RefugeeOrAsylum,
           respiratory,
           AgeGroup10)) %>%
  summary()

```

## Population overview

Number of patients at each age group, and recorded gender.

```{r}
ggplot(population, aes(x = Age, fill=Sex)) +
  geom_histogram(binwidth = 5, boundary = 25) +
  xlab("Age (years)") +
  ggtitle("Patients with ")
```

Total population : `r nrow(population)`



## Respiratory medication & refugee/asylum seeker cross-table

```{r}
age10_conditions_crosstable <- function(population) {
  mc_refugeeorasylum <- as.data.frame.matrix(table(population$AgeGroup10, population$RefugeeOrAsylum)) %>%
    select(Refugee = `TRUE`)
  mc_respiratory <- as.data.frame.matrix(table(population$AgeGroup10, population$respiratory)) %>%
    select(respiratory = `TRUE`)
  mc_conditions <- cbind(mc_refugeeorasylum, mc_respiratory)
  return(mc_conditions)
}

age10_conditions_crosstable(population) %>% 
  mutate(AgeGroup10 = row.names(.)) %>%
  mutate_if(is.numeric, function(x) {color_tile("#DeF7E9", "#71CA97")(x)}) %>%
  select(AgeGroup10, everything()) %>%
  kable("html", align = c("l", rep("r", 8)),
        escape = F) %>%
  kable_styling("hover", full_width = FALSE) %>%
  column_spec(c(2, 3), width = "2cm", width_min = "1.5cm", bold = TRUE) %>%
  add_header_above(c(" ", "Conditions" = 2))

```


## Choosing Phase 1 and Phase 2 groups


```{r}
set.seed(102141)
# set random number seed
# chosen by time on my watch at that particular second

# use 'createDataPartition' function from 'caret' library

# paste which can ignore NA and empty strings
#
# Acts the same as regular paste, unless na.rm = TRUE,
# in which case empty strings and NA are removed
#
# based on code by Moody_Mudskipper at
# https://stackoverflow.com/questions/13673894/suppress-nas-in-paste
# with additional code from
# https://stackoverflow.com/questions/14270950/suppress-separator-in-paste-when-values-are-missing
#
# @param ... the list of strings to paste
# @param sep the separator string, " " by default
# @param collapse the collapse string, NULL by default
# @param na.rm whether to remove NA and empty strings
#
# @return string
paste2 <- function(..., sep = " ", collapse = NULL, na.rm = FALSE){
  # in default case, use paste
  if(!na.rm) return(paste(..., sep = sep, collapse = collapse))
  # cbind is convenient to recycle, it warns though so use suppressWarnings
  dots <- suppressWarnings(cbind(...))
  res <- apply(dots, 1, function(...) {
    x <- c(...)
    x <- x[nchar(x) > 0] # get rid of empty strings
    x <- x[length(x) > 0] # get rid of character(0)
    if (all(is.na(x))) return(c(""))
    do.call(paste, as.list(c(na.omit(x), sep = sep)))
  })
  if(is.null(collapse)) res else
    paste(na.omit(res), collapse = collapse)
}

# balance across possible co-variants of gender, age (10),
# refugee/asylum seeker, BP, antidepressant medication

population <- population %>%
  mutate(Subgroup = paste2(Sex,
                           if_else(RefugeeOrAsylum, "Refugee", as.character(NA)),
                           if_else(respiratory, "Respiratory", as.character(NA)),
                           sep = ", ", na.rm = TRUE)) %>%
  mutate(SubgroupSort = paste(Subgroup)) %>%
  mutate(Subgroup = if_else(Subgroup == "", "None", Subgroup))

phase1 <- NULL
phase2 <- NULL

for (i in sort(unique(population$AgeGroup10))) {
  coinflip <- runif(1)>.5
  for (k in sort(unique(population$SubgroupSort))) {
    subsection <- population[population$AgeGroup10 == i & population$SubgroupSort == k,]
    if (nrow(subsection) > 0) {
      # print(paste(k, ",", i, ":", nrow(subsection)))
      subsection$rank <- runif(nrow(subsection))
      if ((nrow(subsection) %% 2) == 1)
      {coinflip <- 1 - coinflip} # toggle from favouring phase1 or phase2
      new_phase2 <- top_n(subsection, as.integer(nrow(subsection)/2 + coinflip*.5), rank)
      new_phase1 <- anti_join(subsection, new_phase2, by = "ID")
      phase2 <- rbind(phase2, new_phase2)
      phase1 <- rbind(phase1, new_phase1)
    }
  }
}

```

## "Phase 1" group

```{r}
ggplot(phase1, aes(x = AgeGroup10, fill = Subgroup)) +
  geom_histogram(binwidth = 10, boundary = 24.95)
```


## "Phase 2" group

```{r}
ggplot(phase2, aes(x = AgeGroup10, fill = Subgroup)) +
  geom_histogram(binwidth = 10, boundary = 24.95)
```


## Export sub-groups to files for surveyor use.

### Excel file

Re-attach patient names and demographic details to
sub-groups, and export to Excel file (Phase 1 = Treat, Phase 2 = Control) for use by
surveyors.

#### Variables added

* *Ineligible* : reason (if appropriate) ineligible for medication review 
* *Interpreter needed* and *Interpreter used* : indicated in file that interpreter required? interpreter used?
* *Phone Attempts* : Number of phone attempts
* *Message left* : Was message left?
* *Contact made* : was in-person contact made?
* *Decline appointment - why* : reason appointment declined
* *Accepted appointment* : Appointment made at coHealth Kensington for CST?
* *Date of Appt* : Date of appointment made for CST
* *Attended Appt* : Appointment attended?
* *Result* : Result of appointment
* *LMO Review* : Result of LMO review
* *HMR Referral* : Referred for HMR?

```{r eval = FALSE}
# set {r eval = FALSE when 'knitting' to form a HTML file}
# as identifying data should not be in a public space!

RecordingVariables <- matrix(c("Ineligible - reason", "Interpreter needed", "Interpreter used",
                               "Phone attempts", "Message left", "Contact made",
                               "Declined appt - why",
                               "Accepted appt", "Date of appt", "Attended appt",
                               "Review completed", "Result", "LMO Review", "HMR Referral"),
                             nrow = 1, byrow = FALSE)
# list of recording variables to add to Excel sheets

patient_details <- population %>%
  select(ID, Surname, FirstName, KnownAs, Sex, PhoneHW, PhoneM, Address, City, DOB, Age, 
         AgeGroup5, AgeGroup10)
# select columns required for export

phase1_details <- phase1 %>%
  select(ID) %>% 
  # will store AgeGroup5 groups in separate sheets
  left_join(patient_details, by = "ID")

phase2_details <- phase2 %>%
  select(ID) %>% 
  # will store AgeGroup5 groups in separate sheets
  left_join(patient_details, by = "ID")

wb_phase1 <- createWorkbook() # create blank workbook

for (i in sort(unique(phase1_details$AgeGroup5))) {
  subsection <- phase1_details[phase1_details$AgeGroup5 == i,]
  sheetname <- paste("Phase 1 - ", i)
  addWorksheet(wb_phase1, sheetname)
  writeData(wb_phase1, sheetname, subsection %>% select(-c("AgeGroup5", "AgeGroup10")))
  writeData(wb_phase1, sheetname, RecordingVariables, startCol = 13, colNames = FALSE)
}

saveWorkbook(wb_phase1, file = "202003AsthmaCOPDPhase1.xlsx", overwrite = TRUE)

wb_phase2 <- createWorkbook() # create blank workbook

for (i in sort(unique(phase2_details$AgeGroup5))) {
  subsection <- phase2_details[phase2_details$AgeGroup5 == i,]
  sheetname <- paste("Phase 2 - ", i)
  addWorksheet(wb_phase2, sheetname)
  writeData(wb_phase2, sheetname, subsection %>% select(-c("AgeGroup5", "AgeGroup10")))
  writeData(wb_phase2, sheetname, RecordingVariables, startCol = 13, colNames = FALSE)
}

saveWorkbook(wb_phase2, file = "202003AsthmaCOPDPhase2.xlsx", overwrite = TRUE)

```

