---
title: "Cervical Screening 2019"
author: "David Fong"
date: "11th March 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Cervical screening benefits

Regular cervical cancer screening reduces the risk of cancer incidence by approximately a factor of 3 to 4 compared to no screening (for women aged 35 to 79 years), and reduces mortality by a factor of 4 to 10. Regular cervical cancer screening reduces the risk of cervical cancer incidence and death by up to a factor of two compared to irregular cervical cancer screening[^1].

[^1]:“Impact of cervical screening on cervical cancer mortality: estimation using stage-specific results from a nested case-control study” Landy, Pesola, Castanon and Sasieni. British Journal of Cancer (2016) **115**, 1140-1146

## Cervical screening outcome payment

Current eligible practice population : 754 (according to May 2018 PIP data)

Annual outcome payment : $3 per eligible patient = $2262. Never yet received

* Current cervical screening coverage rate (according to 2017 PIP data) = 61.14%
* Target Diabetes SIP claim rate to claim annual outcome payment = 70%

Potential additional Cervical SIP revenue, if target Cervical SIP claim rate achieved, assuming that half of additionally screened women can have a cervical SIP item claimed
= (70-61.14)/100 * 754 * $35 * 0.5 =  $1169.1

Additional revenue if Cervical Outcome Payment achieved
= $2262 (annual outcome payment) + $1169.1 (additional cervical SIP revenue)
= $3431.1

## Cervical Screening and intensive telephone-based case-finding



```{r message=FALSE}
library(tidyverse)
library(dagitty)
```

## Theory of Change graph

```{r}
dag <- downloadGraph("dagitty.net/mannE14") # data for directed acyclic graph model of intervention

```

```{r eval=FALSE, echo=FALSE, fig.width=12, fig.height=8}
# not needed since a more colourful SVG file is used to display the graph
plot(dag)
```

![](cervicalscreeningtelephone.svg)

## Log Frame

-----------------------------------------------------------------------------------
Objectives  Indicator              Verification         Assumptions/Threats
Hierarchy
----------  ---------------------- ----------------     ---------------------------
Inputs      Telephone invitation   Call log             Telephone answered

                                                        Common language used
                                                   
                                                        Social desirability bias?
                                                 
            Letter invitation      Previous letter      Letter read
                                   in file                                            
                                           
                                                        English literacy
                                                        
                                                        Letter persuasive
                                                 
Outputs     Appointments made                           Appropriate cervical
                                                        screening already
                                                        done elsewhere

            Appointments attended                       Appointment is remembered
         
            Cervical screening     Cervical
            (CST) at clinic        screening
                                   results
         
            Cervical screening
            (CST) done elsewhere

Outcome     Improved cervical      Government
            screening coverage     Practice Incentive
                                   Program reports
                                   (PIP statements)
                                
Impact      Reduced cervical                            Vulnerable population
            cancer rates                                screened

-----------------------------------------------------------------------------------
