---
title: "Cervical Screening 2019"
author: "David Fong"
date: "3/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Cervical Screening and intensive telephone-based case-finding



```{r message=FALSE}
library(tidyverse)
library(dagitty)
```

## Theory of Change graph

```{r}
dag <- downloadGraph("dagitty.net/mHMHYZD") # data for directed acyclic graph model of intervention

```

```{r eval=FALSE, echo=FALSE, fig.width=12, fig.height=8}
# not needed since a more colourful SVG file is used to display the graph
plot(dag)
```

![](cervicalscreeningtelephone.svg)

## Log

--------------------------------------------------------------------------------
A        Indicator              Verification         Threats
-------  ---------------------- ----------------     ---------------------------
Inputs   Telephone invitation   Call log             Lack of response

                                                     Lack of common language
                                                 
                                                     Social desirability bias?
                                                 
         Letter invitation      Previous letter      Lack of response
                                in file                                            
                                           
                                                     Lack of English literacy
                                                 
Outputs  Appointments made                           Appointment is forgotten

         Appointments attended
         
         Cervical screening     Cervical
         (CST) at clinic        screening
                                results
         
         Cervical screening
         (CST) done elsewhere

Outcome  Improved cervical      Government
         screening coverage     Practice Incentive
                                Program reports
                                (PIP statements)
                                
Impact   Reduced cervical                            Vulnerable population
         cancer rates                                screened

--------------------------------------------------------------------------------